### 2021-07-21 paper.tex
changed margin from 3cm to 2cm
made the acknowledgement page look a little better by added extra spaces

\usepackage{graphicx}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{multicol}
\usepackage[ddmmyyyy]{datetime}
\usepackage[a4paper, margin=3cm]{geometry}

@@

	I would like to express my special thanks of gratitude to our supervisor
	\textbf{Kajari Bhattacharjeee}, teachers of our department \textbf{Sonali
	Gupta} and department head \textbf{Srijeeta Charkraborty}; as well as our
	principal ma'am \textbf{Dr. Mausumi Chatterjee} who gave us the golden
	opportunity to do this wonderful project on \textit{Brain tumor detection},
	which has also helped us in doing a lot of research and we came to know
	about many new things.

>>>>

\usepackage{graphicx}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{multicol}
\usepackage[ddmmyyyy]{datetime}
\usepackage[a4paper, margin=2cm]{geometry}

@@

	I would like to express my special thanks of gratitude to our supervisor
	\textbf{Kajari Bhattacharjeee}, teachers of our department \textbf{Sonali
	Gupta} and \textbf{Srijeeta Charkraborty} ( current department head ); as
	well as our principal ma'am \textbf{Dr. Mausumi Chatterjee} who gave us the
	golden opportunity to do this wonderful project on \textit{Brain tumor
	detection}, which has also helped us in doing a lot of research and we came
	to know about many new things.
